Making multiple-locus association mapping on a genome-wide scale routine

### 2017-10-16 AM+draft.tex
161017 Working on methods  section

\subsubsection{The specifics}
The Eagle approach for multiple-locus association mapping is based on building a linear mixed model, iteratively, via forward 
selection.  Suppose $s$ iterations of our model building process have already been performed. 
The next iteration is performed as follows. First, we fit the current model to the data. The model is of the form 
\begin{equation}
y = X \tau + u_g + e
\end{equation}
where $y^{(n \times 1)}$ is a vector containing the quantitative trait values observed from $n$ individuals, 
$X^{(n \times p)}$ is a known design matrix of full rank, 
$\tau^{(p \times 1)}$ is a vector of $p$ fixed effects parameters, 
$u_g^{(n \times 1)}$ is a vector 
of genetic effects, and 
$e^{(n \times 1)}$ is a vector of residuals whose distribution is assumed to follow $N(0, \sigma^2_e I^{(n \times n)})$.

Suppose phenotypic and genotypic data are collected from a genome-wide association study involving $n$ individuals. 
Let $Y^{(n \times 1)}$ be a vector containing the quantitative trait data. Also, let $M^{(n \times L)}$ be a matrix of snp genotypes which have been collected from the $n$ individuals across $L$ snp loci. $M$ contains values -1, 0, and 1 corresponding to snp genotypes AA, AB, and BB, respectively.

To identify genomic regions which contain genes that influence the trait

We map genomic regions containing genes that influence the trait

>>>>

\subsubsection{The specifics}

%%Suppose data are collected from a genome-wide association study.  The study involves $n$ individuals. 
%Let $y^{(n \times 1)}$ be the vector containing the quantitative trait data. 
%Let $M^{(n \times L)} = [m_1 m_2 \ldots m_L]$ be the matrix containing the genotype data. Snp genotypes 
%are collected from $L$ loci. The vector $m_j^{(n \times 1)}$ contains the snp genotypes for the $j$th snp. The genotypes 
%are recoded as -1, 0, and 1 corresponding to snp genotypes AA, AB, and BB, respectively.

The Eagle approach for multiple-locus association mapping is based on building a linear mixed model, iteratively, via forward 
selection.  Suppose $s$ iterations of our model building process have already been performed. This means $s$ snp-trait 
associations which identify $s$ separate genomic regions of interest have been found.  To perform the $s+1$ iteration of 
our model building procedure, we perform the following.

First, we fit the current model to the data. 
Let $y^{(n \times 1)}$ be the vector containing the quantitative trait data. 
Let $M^{(n \times L)} = [m_1 m_2 \ldots m_L]$ be the matrix containing the genotype data which has been collected 
from $L$ loci that span the genome. Here, the vector $m_j^{(n \times 1)}$ contains the $j$th snp genotypes for the $n$ individuals. 
The genotypes are coded as -1, 0, and 1 corresponding to snp genotypes AA, AB, and BB, respectively.

The model is of the form 
\begin{equation}
y = X \tau + u_g + e
\end{equation}
where 
$X^{(n \times p)}$ is a known design matrix of full rank and may contain data on non-genetic effects such as age and height 
or principal component values to account for population structure (ref). The vector 
$\tau^{(p \times 1)}$ has $p$ fixed effects parameters. The vector 
$u_g^{(n \times 1)}$ contains the 
genetic effects. The vector of residuals is 
$e^{(n \times 1)}$ whose distribution is assumed to follow $N(0, \sigma^2_e I^{(n \times n)})$.

Up to this point,  this model differs little from standard linear mixed models for association mapping (refs). 
However, 
it is how we specify $u_g$ that distinguishes our model from others. The genetic effects $u_g$ are modelled as
